\documentclass[letterpaper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \usepackage[left=0.25in,right=0.25in,top=0.75in,bottom=0.75in]{geometry}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Michael Bartlett Resume},
    pdfpagemode=FullScreen,
    }

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
    {\fontsize{17.28pt}{20pt}\selectfont \scshape {Michael Bartlett}}\\
    \href{mailto:bartlett.michael17@gmail.com}{bartlett.michael17@gmail.com} $\cdot$ \href{tel:4845535847}{(484) 553-5847} $\cdot$ \href{http://michaelbartlett.me}{michaelbartlett.me} \href{https://www.linkedin.com/in/michaelbartlett17/}{linkedin.com/in/michaelbartlett17} \\
\end{center}

%==== Education ====%
\header{Education}
\textbf{University of Pittsburgh}\hfill Pittsburgh, PA\\
B.S. Computer Science \& Information Science Minor\\
% \begin{tabular}{@{} l l }
% Relevant Coursework: & Intermediate Programming, Algorithms \& Data Structures, \\
% & Formal Methods in Computer Science
% \end{tabular}
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Honestly} \hfill Remote\\
\textit{Lead Full-stack Developer} \hfill August 2024 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
    \item Engineered and implemented several new features and client-specific integrations, including a Salesforce data integration for a headless Wordpress site, enhancing platform functionality and data flow.
    \item Contributed to the large-scale refactoring of a legacy vanilla PHP application (circa 2005) to a modern PHP 8.4 codebase with an ORM, enhancing application architecture and performance.
    \item Resolved critical search performance issues by migrating a frontend-bound search to a backend REST API implementation with filtering and sorting, eliminating server crashes and improving user experience.
    \item Implemented and managed GitHub Actions for CI/CD and established Docker development environments, streamlining workflows and improving team efficiency.
    \item Engineered and maintained client applications on AWS infrastructure (EC2, Lightsail, RDS), utilizing diverse technical stacks including Node.js, React.js, Next.js, NestJS, WordPress, and Laravel.
\end{itemize}
\vspace{-1mm}
\textbf{eServices Payment Technology} \hfill Baldwin, PA\\
\textit{Full-stack Software Engineer} \hfill May 2022 - August 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
    \item Led design and implementation of critical new features, while also migrating legacy features from a legacy PHP application, to a modern, high-performance React/Redux and Node.js web application.
    \item Proactively resolved 90\% of client and staff support requests for 1500+ clients and 15+ employees, providing training and troubleshooting to ensure user satisfaction.
    \item Assisted in leading a team of engineers and collaborated with CTO on key technical decisions.
    \item Optimized database queries and backend processes, resulting in improved application performance and reduced response times.
    \item Demonstrated proficiency in SQL Server, Node.js, Docker, GitHub Actions, and Windows Server administration.
\end{itemize}
\vspace{-1mm}
\textbf{D.E. Shaw \& Co} \hfill New York, NY\\
\textit{Sytems Administrator Intern} \hfill June 2023 - August 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Developed and implemented a solution for proactive monitoring of common Outlook issues, significantly reducing helpdesk tickets and improving user experience.
	\item Streamlined manual processes through Slack-based automation, enhancing team efficiency and saving valuable time.
	\item Partnered effectively with a Systems Administrator team to provide comprehensive support for over 3000 employees.
	\item Troubleshooted and resolved technical issues for Windows and Linux systems and applications, ensuring optimal functionality.
	\item Leveraged PowerShell, Python, and Kubernetes to develop innovative solutions and drive impactful improvements.
\end{itemize}
\vspace{-1mm}
\textbf{Freelance Work} \hfill Remote \\
\textit{Web Development Consulting} \hfill May 2020 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Designed and developed custom WordPress websites, plugins, and features for diverse clients.
	\item Collaborated closely with clients to deliver tailored website solutions aligned with their goals.
	\item Manage website hosting, domains, DNS records, and email configurations through cPanel, utilizing Linux, MySQL, and other relevant technologies.
	\item Implement best practices to optimize website speed, security, and overall performance for a seamless user experience.
	\item Advise clients on strategies to enhance their online presence through social media, Google My Business, and other relevant channels.
\end{itemize}

\header{Strengths \& Technical Skills}
\begin{tabular}{ l p{0.69\textwidth} }
	Programming \& Query Languages: & JavaScript/TypeScript, PHP, Python, Java, PowerShell, HTML/CSS, SQL \\
    Databases:                       & SQL Server, MySQL, PostgreSQL \\
    Libraries \& Frameworks:         & Node.js, Express.js, React.js, Redux.js, NestJS, Material-UI, Laravel, Flask \\
	Technologies:                   & REST APIs, Git, Github, MacOS, Windows, Linux, Kubernetes, Docker, AWS (EC2, RDS, ECS, ECR, Route53, CloudWatch) \\
    Technical Skills:              & Web Development, Systems Administration, Automation, Troubleshooting, CI/CD \\
    Strengths:                      & Self-starter, Problem Solver, Communication, Adaptability, Teamwork, Time Management \\
\end{tabular}
\vspace{2mm}


\
\end{document}
